---
title: "Geospatial Analysis Portfolio"
author: "Katherine M. Yut"
date: '`r format(Sys.Date(),format="%A, %B %d, %Y")`'
output:
  pdf_document: default
  html_document:
    df_print: paged
    fig_caption: true
    highlights: pygments
    number_sections: no
    theme: spacelab
    toc: yes
    toc_float: yes
  word_document: default
urlcolor: blue
toc: yes
toc_float: yes
indent: yes
fontsize: 12pt
header-includes:
  - \usepackage[export]{adjustbox}
  - \usepackage{pdfpages}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Load packages
library(ggplot2)
library(kableExtra)

# Cover letter mad libs
recruiter <- ""
company <- "NASA"
position <- "Program Scientist"

# With a background in n1, n2, and n3, I possess strong sk1 coupled with sk2, making me an ideal candidate for data-driven endeavors.
n1 <- "data wrangling" 
n2 <- "geospatial analysis" 
n3 <- "the art of data visualization" 

sk1 <- "problem-solving abilities"
sk2 <- "a knack for coding"
```

***

\pagebreak

# Cover Letter

\noindent Dear `r company`,  
<br />  
\indent I am writing to express my interest in the `r position` position  at `r company` and outline my qualifications, which firmly position me as an outstanding potential team member. With a background in `r n1`, `r n2`, and `r n3`, I possess strong `r sk1` coupled with `r sk2`, making me an ideal candidate for data-driven endeavors.    
<br />   
\indent During my tenure as a GIS & Energy Data Analyst at the University of Texas, Bureau of Economic Geology, I have honed comprehensive skills in GIS, coding, and effective communication. My track record includes successfully utilizing tools such as ArcMap and R to perform intricate subsurface research, develop peer-reviewed literature, and present findings.  
<br />   
\indent My experience as a Viticulture Research GIS Intern at E. & J. Gallo Winery has equipped me with the proficiency to manage large datasets, automate satellite data acquisition, and employ statistical techniques to drive decision-making. Collaborating with cross-functional teams, I contributed to optimizing wine grape yield and quality through informed irrigation strategies, solidifying my dedication to translating data into impactful solutions.  
<br />   
\indent While a remote sensing intern with NASA DEVELOP, I conducted thorough literature reviews, collected training data, deployed classification models, and performed site suitability analyses. My role demanded a keen eye for design as I created compelling visuals while ensuring adherence to stringent style guidelines. I excelled at developing workflows using ArcGIS, ENVI, Idrisi Terrset, and Google Earth Engine despite unforeseen challenges. Thriving in a collaborative environment, my team and I effectively communicated complex scientific concepts to both technical and non-technical audiences.  
<br />   
\indent My educational background, consisting of a Master of Arts in Economics and Big Data, a Bachelor of Arts in Economics and Big Data, and a Bachelor of Science in Geographic Information Science, demonstrates my curiosity, rapid learning capability, and unwavering commitment to acquiring expertise across domains. My skill set includes RStudio, R, ESRI ArcMap, QGIS, Google Earth Engine, ENVI, GitHub, Java, JavaScript, SQL, and Python.  
<br />   
\indent Driven by a genuine passion for data analysis, I am eager to contribute my insights, skills, and efficiency to the team. Thank you for considering my application. I look forward to the opportunity to discuss how my experiences align with your vision during an interview.  
<br />    
\noindent Best,  
\includegraphics[width=1.75in]{pdf_files/signature.png}  
\noindent Katherine (Katy) Yut  


<!-- # Resume -->
\includepdf[pages={1}]{YutK_resume_dec2022_v2.pdf}

\pagebreak

# References

The following individuals are happy to vouch for my character and data analysis capabilities:

1.  Katie Smye  
    Bureau of Economic Geology | Research Associate  
    katie.smye@beg.utexas.edu | (512)-471-6775  

2.  Brent Sams  
    E. & J. Gallo Winery | Research Scientist   
    sams.brents@gmail.com | (209) 568-9317

3.	Kirsten de Beurs  
    Wageningen University | Chair & Professor     
    kdebeurs@gmail.com | +3 (131) 748-2219


\pagebreak


# Sample Work

### Bureau of Economic Geology

\begin{center}
\includegraphics[width=6.5in]{pdf_files/11102022_PM_Water_Cut_Katie_lowRes.jpg}
\end{center}

> *Figure 1: Map of Water Cut (Produced Water / Produced Oil + Produced Water) for all horizontal wells in the Permian Basin, aggregated on square mile blocks. Created in ArcMap using data from IHS Enerdeq.*  

\pagebreak

\includegraphics[width=6.5in]{pdf_files/11142022_MB_DB_HV_Cum_Prod_BOE_Katy_lowRes.jpg}

> *Figure 2: Map of total cumulative production of oil and gas production, in barrels of oil equilvalent, for all horizontal wells in Delaware, Midland, and Haynesville, aggregated on square mile blocks. Created in ArcMap using data from IHS Enerdeq.*  

\begin{center}
\includegraphics[width=6.5in]{pdf_files/10062022_PM_All_Wells_Completion_Date_Tim_lowRes.jpg}
\end{center}

> *Figure 3: Map of all wells drilled in the Permian Basin region, colored by decade completed. Created in ArcMap using data from IHS Enerdeq.*

## Internships

### E&J Gallo Winery (2020)
  
\includegraphics[width=6.5in]{pdf_files/Alberti_lowRes.png}  

> *Figure 4: Kriging interpolated Brix (i.e., grape sugar content) values for 2017, 2018, and 2019 across a single block with sampling algorithm solutions for both Landsat and Sentinel imagery. Created in QGIS.*  

\pagebreak

### NASA DEVELOP (2019)  

Forecasting Red Spruce Restoration Using NASA Earth Observations to Support Decision Making in the USFS Monongahela National Forest  
<br />

> **ABSTRACT**: In the Monongahela National Forest (MNF), situated in the Allegheny Highlands of West Virginia, extensive logging and mining practices have significantly altered the structure and composition of flora and fauna over the past two centuries. To aid red spruce restoration, this study mapped current and historical stands and identified non-native stands... [Read full abstract here.](https://develop.larc.nasa.gov/2019/summer/MonongahelaNationalForestEco.html)

\includegraphics[width=6.5in]{pdf_files/NASAFig.png}

> *Figure 5: Land classification change using Classification Tree Algorithm in Idrisi Terrset (left). Site suitability analysis created in ArcMap (right).*

***

\pagebreak

# Relevant Coursework 

```{r echo=FALSE, fig.width=8, fig.height=5}
# Assign variables
sem <- c("Fall 2016", "Spring 2017", "Fall 2017", "Spring 2018", "Fall 2018", 
         "Spring 2019", "Fall 2019", "Spring 2020", "Sum 2020", "Spring 2021")
num <- c(0, 0, 0, 0, 1, 0, 2, 4, 1, 3)
ord <- 1:10
cum <- cumsum(num)

# Merge into dataframe
df <- data.frame(ord, sem, num, cum)
df$sem <- factor(df$sem, levels = df$sem[order(df$ord)])

# Plot time series
ggplot(data=df) +
  geom_area(aes(x=sem, y=cum, group=1), fill="grey") +
  geom_col(aes(x=sem, y=num, group=1), width=0.2) + 
  scale_y_continuous(breaks = 0:11) +
  labs(title="Data Analysis Experience", 
       subtitle="R Courses Taken in College", 
       x="Semester", 
       y="Count") 
```
           
> *Figure 6: Time series by semester showing cumulative (light grey) and count (dark grey) of RStudio data science classes taken. Created in RStudio using ggplot2.*  


```{r echo=FALSE, fig.width=8, fig.height=5, warning=F}
# Assign variables
name <- c("Econometrics", "Spatial Statistics", "Stats for Decision Making", 
          "Advanced GIS/Spatial Analysis", "Managerial Econ II", "Geoinformatics Capstone Seminar", 
          "Bayesian Econometrics", "Intro to Math Stats", "Text Analytics", "Advanced Applied Stats", "Research in Economic Problems")
grade <- c("A", "A", "A", "A", "A", "A", "B", "A", "A", "A", "Pass")
sem <- c("Fall 2018", "Fall 2019", "Fall 2019", "Spring 2020", "Spring 2020", "Spring 2020", 
         "Spring 2020", "Summer 2020", "Spring 2021", "Spring 2021", "Spring 2021")

# Merge into dataframe
df2 <- data.frame(name, grade, sem)

# Create table
df2 %>%
  kbl(booktabs = T, linesep = "",
      col.names=c("Course Name", "Grade", "Semester"),
      align=c('l', 'c', 'l')) %>%
  kable_paper(full_width = F) %>%
  kable_styling(latex_options = c("hold_position", "striped"), stripe_index = c(1, 4:7, 9:11)) %>%
  column_spec(2, bold = T, color = c(rep("OliveGreen", 6), "Mahogany", "OliveGreen", "OliveGreen", "OliveGreen", "gray"))
```
  
> *Table 1: Table of each RStudio data science class and the grade earned. Created in RStudio using kableExtra.*  
